Funding programmes for early career researchers do/not influence their independence

### 2023-06-09 article.Rmd
new developments in article

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
library(dplyr)
library(cobalt)
library(knitr)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
library(dplyr)
library(cobalt)
library(knitr)
library(psych)
library(kableExtra)
```

@@

### Before intervention

```{r echo=FALSE}

# assuming df is your dataframe
df <- r_before_final

# list of numeric columns. Exclude treatment column
numeric_vars <- df %>% select(where(is.numeric)) %>% select(-weights, -funded_control, -id, -treatment_year, -career_start_year) %>% names()

# descriptive stats for treatment level 1
table_before_1 <- df %>% filter(treatment == 1) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)

# Print table for treatment level 1
kable(table_before_1, digits = 3, caption = "Descriptive statistics for treatment group") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# descriptive stats for treatment level 0
table_before_0 <- df %>% filter(treatment == 0) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)

# Print table for treatment level 0
kable(table_before_0, digits = 3, caption = "Descriptive statistics for unfunded control group") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# descriptive stats for treatment level 2
table_before_2 <- df %>% filter(treatment == 2) %>% select(all_of(numeric_vars)) %>% describe() %>% select(n, mean, sd, min, max) %>% round(., digits = 3)

# Print table for treatment level 2
kable(table_before_2, digits = 3, caption = "Descriptive statistics for funded control group") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

### After intervention

```{r echo=FALSE}
d <- tar_read(full_indicator)
na_counts <- sum(is.na(d$RII))
